---
title: "Australian Election Study"
author: "Annie Chen"
date: "4/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, haven)
```

AES contains both Voter studies as well as Candidate studies

What can we learn from these surveys?

```{r}
#Australian Election Study, 1987-2016 Trends
path <- "~/Dropbox/Thesis/inc_adv/raw_data"
statadata <- function(file_name) {
  read_dta(paste0(path, "/surveys/", file_name))
}

# all files in this folder 
all_year <- list.files(file.path(path, "/surveys"), pattern = ".dta")
  
# read in all the data
data <- list()
data <- sapply(X = all_year, FUN = statadata)
  
# remove .csv from names
names(data) <- sapply(1:length(all_year), 
                      function (x) str_split(all_year, pattern = "\\.")[[x]][1])

```


### 2019

Create a data frame for MRP.

```{r}
mrp_data_fxn <- function (data) {
  attach(data$AES_2019)
  out <- data.frame(
     age = AGE,
     gender = dem_gen_16,
     religion = H6,
     married = H8,
     education = G3,
     income = J6,
     housing = dem_home,
     state = STATE,
     division = CED_AEC,
     pid = B1,
     pid_strendth = B2,
     weights = wt_pooled
     )
  return(out)
}
colnames(data$AES_2016)
#data$AES_2019$H19STATE

mrp_data_fxn(data$AES_2019)
```





Party identification:

1 -- Liberal 
2 -- Australian Labor Party
3 -- National Party of Australia
```{r}
aes_trends <- data.frame(
  pid = c(
  data$AES_2001$B1,
  # 8 = no party
  data$AES_2004$b1,
  # 8 = no party
  data$AES_2007$b1,
  # 6 = no party
  data$AES_2010$b1,
  # 6 = no party
  data$AES_2013$b1,
  # 6 = no party
  data$AES_2016$B1,
   # 6 = no party
  data$AES_2019$B1
))
```






# AES Candidate Surveys

Use these distributions in the conjoint for more external validity. Personal data is restricted, but there are aggregate variables. Cross reference this with first preference data. 

- A7b:	Were you ever employed as a State or Federal party official?
- A7c: Did you ever hold any elected position within the party organisation?

- F1: In what year were you born? (*see Age_group variable*)

- F5: How many years of tertiary study have you completed since you left secondary school? (this means after high school in Australia) 

- F10:	What is your current occupation? (If you are a member of parliament and/or retired: What was your former occupation?)



```{r}
acs_data <- read_dta("~/Documents/GitHub/annie_better_document_your_stuff/data/acs19_unrestricted.dta")

glimpse(cs_data)
qplot(cs_data$A10)

acs <- acs_data %>% 
  mutate(age_group = case_when(Age_group == 1 ~ "18-24", #21
                               Age_group == 2 ~ "25-34", #30
                               Age_group == 3 ~ "35-44", #40
                               Age_group == 4 ~ "45-54", #50
                               Age_group == 5 ~ "55-64", #60
                               Age_group == 6 ~ "65+"), #70
         educyrs_group = case_when(F5COND == 0 ~ "0",
                                   F5COND == 1 ~ "1-2",
                                   F5COND == 2 ~ "3-4",
                                   F5COND == 3 ~ "5-6",
                                   F5COND == 4 ~ "7+"),
         occup_group = case_when(F10COND == 1 ~ "Managers",
                                   F10COND == 2 ~ "Professionals",
                                   F10COND == 3 ~ "Technicians and Trades Workers",
                                   F10COND == 4 ~ "Community and Personal Service Workers",
                                   F10COND == 5 ~ "Clerical and Administrative Workers",
                                   F10COND == 6 ~ "Sales Workers",
                                   F10COND == 7 ~ "Machinery Operators and Drivers",
                                   F10COND == 8 ~ "Labourers",
                                   F10COND == 9 ~ "Other")) 
```



### AGE conjoint correspondence:

- 31 = 25-34 (0.10)

- 42 = 35-44 (0.18)

- 53 = 45-54 (0.25)

- 64 = 55-64 (0.30)

- 75 = 65+ (0.17)

```{r}
### age distribution
qplot(acs$age_group)
# in conjoint, use the median of the age group as age level
# i.e., median of 18-24 is 21 
prop.table(table(acs$age_group))
# each age drawn with the following probabilities
```


### EDUCATION conjoint correspondence:

- Managers = Business executive

- Professionals = Lawyer



```{r}
#education distribution
qplot(acs$educyrs_group)
# in conjoin, use the low end: (0, 1, 3, 5, 7)
prop.table(table(acs$educyrs_group))
```



### OCCUPATION conjoint correspondence:

- Business executive = Managers

- Lawyer = Professionals

- ...

```{r}
#occupation distribution
qplot(str_wrap(acs$occup_group, width = 20)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# there are too many groups here, will need to condense (or just omit this)
prop.table(table(acs$occup_group))
```


GENDER (according to 2010 distribution)

- Female = Female (27%)

- Male = Male (73%)


