---
title: "tests"
author: "Annie"
date: "4/23/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

MANIPULATION ##################################################################


Basic Binomial test
```{r}
#when restrict the margin of victory to 2% bandwidth
#right of cutoff
data_candidateB$margin[data_candidateB$margin < 0.02 & data_candidateB$margin > 0]
#27 observations
#left of cutoff
data_candidateB$margin[data_candidateB$margin > -0.02 & data_candidateB$margin < 0]
#34 observtaions

binom.test(27, 61, 1/2)
#p-value is 0.44 (no sorting)


#when restrict the margin of victory to 5% bandwidth
#right of cutoff
data_candidateB$margin[data_candidateB$margin < 0.05 & data_candidateB$margin > 0]
#63 observations
#left of cutoff
data_candidateB$margin[data_candidateB$margin > -0.05 & data_candidateB$margin < 0]
#79 observtaions

binom.test(63, 142, 1/2)
#p-value is 0.44 (no sorting)
```

McCrary Density Test
```{r}

DCdensity(runvar = data_candidateB$margin,  bw = bandwidthB, cutpoint = 0, plot = FALSE, ext.out = TRUE)


myDCdensity <- function(runvar, cutpoint, bw = bandwidthB, my_abline = 0, my_title = "Default"){

  # get the default plot
  myplot <- DCdensity(runvar, cutpoint, bw = bandwidthB, plot = TRUE)

  # 'additional graphical options to modify the plot'
  abline(v = my_abline, lty=2)
  title(main = my_title)

  # return
  return(myplot)
}

#McCrary
t<- DCdensity(runvar = data_candidateB$margin, bw = bandwidthB, cutpoint = 0, ext.out=TRUE, plot = FALSE)$theta
se<- DCdensity(runvar = data_candidateB$margin,  bw = bandwidthB, cutpoint = 0, ext.out=TRUE, plot = FALSE)$se
myDCdensity(runvar = data_candidateB$margin, cutpoint = 0,  my_abline = 0, my_title = "p= 0.124")
```


Histogram of number of observations
```{r}
ggplot(data = dplyr::filter(data_candidateB, inc == 1 & margin <0.2 & margin > -0.2),
       aes(x= margin)) +
  geom_histogram(binwidth = 0.01)+
  geom_vline(xintercept = 0, lty = 2, col= "red") +
  labs(x = "Incumbent Margin of Victory", y = "# of observations")+
  theme_bw(
  )

hist(dplyr::filter(data_candidateB, inc == 1 & margin <0.3 & margin > -0.3)$margin,
     main = "Incumbent Imbalance", ylab= "# of observations", xlab = "Incumbent Margin of Victory", 
     breaks = 30) + abline(v = 0, col = "blue", lwd = 1.5)
# left = 6, right = 14 (0.01)
# left = 14, right = 21 (0.02)
```


Cattaneo, Idrobo, Titiunik (2018) density test
```{r}
summary(rddensity(data_candidateB$margin))
summary(rddensity(data_candidateB$margin, 
                  p = 1, c = 0,kernel = "triangular"))


test<-rddensity(data_candidateB$margin, c = 0, p = 1, 
                h = bandwidthB,
                kernel = "triangular", all = TRUE)
summary(test)

rdplotdensity(test, na.omit(data_candidateB$margin), plotGrid = "qs",
              plotN = 25,
              title = "Party-level CIT (2017a) Density Test", xlabel = "Margin of Victory \n (Robust p-value = 0.41)", ylabel = "Density", type = "both")
```


PLACEBO ##################################################################

Placebo cutoffs (margin of victory at 10% and 5%)
```{r}
est <- vector()
lower <- vector()
upper <- vector()
bandw <- vector()
nobsl <- vector()
nobsr <- vector()

placecut10 <- rdrobust(data_candidateB$Wint1, 
                       data_candidateB$margin,
                       covs = data_candidateB$inc,
                       p = 1, c = 0.1,
                       kernel = "triangular")
summary(placecut10)
est[1]<- placecut10$coef[2]
lower[1] <- placecut10$ci[3,1]
upper[1] <- placecut10$ci[3,2]
bandw[1] <- placecut10$bws[1]
nobsl[1] <-placecut10$Nh[1]
nobsr[1] <-placecut10$Nh[2]
  
placecut5 <-rdrobust(data_candidateB$Wint1,
                     data_candidateB$margin, 
                     covs = data_candidateB$inc,
                     p = 1, c = 0.05,kernel = "triangular")
est[2]<- placecut5$coef[2]
lower[2] <- placecut5$ci[3,1]
upper[2] <- placecut5$ci[3,2]
bandw[2] <- placecut5$bws[1]
nobsl[2] <- placecut5$Nh[1]
nobsr[2] <-placecut5$Nh[2]
  
placecut2 <- rdrobust(data_candidateB$Wint1,
                       covs = data_candidateB$inc,
                      data_candidateB$margin, p = 1, c = 0.02,kernel = "triangular")
est[3]<- placecut2$coef[2]
lower[3] <- placecut2$ci[3,1]
upper[3] <- placecut2$ci[3,2]
bandw[3] <- placecut2$bws[1]
nobsl[3] <- placecut2$Nh[1]
nobsr[3] <-placecut2$Nh[2]

placecut0 <- rdrobust(data_candidateB$Wint1,
                      data_candidateB$margin, 
                      covs = data_candidateB$inc,
                      p = 1, c = 0, kernel = "triangular")
est[4]<- placecut0$coef[2]
lower[4] <- placecut0$ci[3,1]
upper[4] <- placecut0$ci[3,2]
bandw[4] <- placecut0$bws[1]
nobsl[4] <-placecut0$Nh[1]
nobsr[4] <-placecut0$Nh[2]
    
placecut_10 <- rdrobust(data_candidateB$Wint1,
                        data_candidateB$margin, 
                        covs = data_candidateB$inc,
                        p = 1, c = -0.1,kernel = "triangular")
est[5]<- placecut_10$coef[2]
lower[5] <- placecut_10$ci[3,1]
upper[5] <- placecut_10$ci[3,2]
bandw[5] <- placecut_10$bws[1]
nobsl[5] <-placecut_10$Nh[1]
nobsr[5] <-placecut_10$Nh[2]
  
placecut_5 <- rdrobust(data_candidateB$Wint1,
                       data_candidateB$margin, 
                       covs = data_candidateB$inc,
                       p = 1, c = -0.05,kernel = "triangular")
est[6]<- placecut_5$coef[2]
lower[6] <- placecut_5$ci[3,1]
upper[6] <- placecut_5$ci[3,2]
bandw[6] <- placecut_5$bws[1]
nobsl[6] <-placecut_5$Nh[1]
nobsr[6] <-placecut_5$Nh[2]
  
placecut_2 <- rdrobust(data_candidateB$Wint1,
                       data_candidateB$margin, 
                       covs = data_candidateB$inc,
                       p = 1, c = -0.02,kernel = "triangular")
est[7]<- placecut_2$coef[2]
lower[7] <- placecut_2$ci[3,1]
upper[7] <- placecut_2$ci[3,2]
bandw[7] <- placecut_2$bws[1]
nobsl[7] <-placecut_2$Nh[1]
nobsr[7] <-placecut_2$Nh[2]
placecut <- data.frame(est, 
                       CI = paste(round(lower, 2), round(upper, 2), sep = ", "), 
                       bandw, cutoff = c(-0.1, -0.05, -0.02, 0, 0.02, 0.05, 0.1), 
                       obs = paste(nobsl,nobsr, sep = ", "))

library(kableExtra)
kable(placecut, col.names = c("RD Estimate", "Confidence Intervals", 
                              "Optimal Bandwidth", "Alternative Cutoff", 
                              "Observations (L/R)")) %>% kable_styling()


ggplot(data= placecut, aes(x = cutoff, y= est)) +
  geom_point() +
  geom_errorbar(ymin=lower, ymax=upper, width = 0.0025) +
  scale_y_continuous(limits = c(-1, 1)) +
  geom_hline(yintercept = 0, lty = 2, col = "red") +
  labs(x = "Cutoff", y = "RD Estimate (Pr(Winning))", title = "Party-level: Placebo Test of Different Cutoffs") +
  theme_bw()
```

Placebo Tests on pre-treatment covariates  (local linear)
```{r}
### open seat (t)
ll.placeopen.5 <- rdrobust(y=data_candidateB$openseat,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
popen5 <- ll.placeopen.5$pv[3]
ll.placeopen.opt <- rdrobust(y=data_candidateB$openseat,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
popenmpt <- ll.placeopen.opt$pv[3]


### win (t-1)
ll.placew.5 <- rdrobust(y=data_candidateB$Wint_1,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pw5 <- ll.placew.5$pv[3]
ll.placev.5 <- rdrobust(y=data_candidateB$VPt_1,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pv5 <- ll.placev.5$pv[3]

### vote share (t-1)
ll.placew.opt <- rdrobust(y=data_candidateB$Wint_1,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pwopt <- ll.placew.opt$pv[3]
ll.placev.opt <- rdrobust(y=data_candidateB$VPt_1,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pvopt <- ll.placev.opt$pv[3]

### ALP incumbent (t)
ll.placeinc.5 <- rdrobust(y=data_candidateB$inc,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pinc5 <- ll.placeinc.5$pv[3]
ll.placeinc.opt <- rdrobust(y=data_candidateB$inc,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pincopt <- ll.placeinc.opt$pv[3]

### LIB/NAT incumbent (t)
ll.placeincL.5 <- rdrobust(y=data_candidateB$incLIB,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pincL5 <- ll.placeincL.5$pv[3]
ll.placeincL.opt <- rdrobust(y=data_candidateB$incLIB,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pincLopt <- ll.placeincL.opt$pv[3]


### length of time party was in power in that division  (t)
ll.placePRE.5 <- rdrobust(y=as.numeric(data_candidateB$Prev_TermsALP),
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pPRE5 <- ll.placePRE.5$pv[3]
ll.placePRE.opt <- rdrobust(y=as.numeric(data_candidateB$Prev_TermsALP),
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pPREopt <- ll.placePRE.opt$pv[3]


### turnout (t)
ll.placeturn.5 <- rdrobust(y=as.numeric(data_candidateB$TurnoutPercentage),
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pturn5 <- ll.placeturn.5$pv[3]
ll.placeturn.opt <- rdrobust(y=as.numeric(data_candidateB$TurnoutPercentage),
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pturnopt <- ll.placeturn.opt$pv[3]



### campaign donations (t)
ll.placedon.5 <- rdrobust(y=data_candidateB$donations,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pdon5 <- ll.placedon.5$pv[3]
ll.placedon.opt <- rdrobust(y=data_candidateB$donations,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pdonopt <- ll.placedon.opt$pv[3]


### campaign spending (t)
ll.placespend.5 <- rdrobust(y=data_candidateB$spending,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pspend5 <- ll.placespend.5$pv[3]
ll.placespend.opt <- rdrobust(y=data_candidateB$spending,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
pspendopt <- ll.placespend.opt$pv[3]


### partisanship
ll.placeparty.5 <- rdrobust(y=data_candidateB$ALPsupport,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)
pparty5 <- ll.placeparty.5$pv[3]
ll.placeparty.opt <- rdrobust(y=data_candidateB$ALPsupport,
           x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)
ppartyopt <- ll.placeparty.opt$pv[3]


#### put into table
bt <- data.frame(variable = c("Win (t-1)", "Win (t-1)", 
                              "Vote share (t-1)","Vote share (t-1)",
                              "Open seat",   "Open seat",
                              "ALP incumbent","ALP incumbent",
                              "LIB/NAT incumbent","LIB/NAT incumbent",
                              "Donations","Donations",
                              "Spending", "Spending",
                              "ALP previous terms", "ALP previous terms",
                              "Turnout","Turnout",
                              "Partisan Support", "Partisan Support"),
                 value = c(pw5,pwopt, 
                           pv5, pvopt, 
                           popen5, popenopt,
                           pinc5, pincopt,
                           pincL5, pincLopt,
                           pdon5, pdonopt,
                           pspend5, pspendopt,
                           pPRE5, pPREopt,
                           pturn5, pturnopt,
                           pparty5, ppartyopt),
                 shape = c(
                           "5%", "optimal", 
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal",
                           "5%", "optimal"
                           ))

bt$variable <- factor(bt$variable, levels=rev(unique(bt$variable)))


ggplot(data = bt) +
  geom_point(aes(x = value, y = variable, shape = shape)) +
  labs(x = "p-value", y = "Pre-treatment Variables", title = "Party-level: Placebo Tests on Pre-treatment Variables",
       shape = "Bandwidth")+
  geom_vline(xintercept = 0.05, lty = 2) +
  theme_bw()


```


Placebo plots
```{r}
#openseats
rdplot(data_candidateB$openseat[abs(data_candidateB$margin) <= bandwidthB], data_candidateB$margin[abs(data_candidateB$margin) <= bandwidthB],
       p = 1, kernel = "triangular",  
       x.label= "Margin of victory (t)",
       y.label = "Open seat")

# wIN (t-1)
rdplot(data_candidateB$Wint_1[abs(data_candidateB$margin) <= bandwidthB], data_candidateB$margin[abs(data_candidateB$margin) <= bandwidthB],
       p = 1, kernel = "triangular",  
       x.label= "Margin of victory (t)",
       y.label = "Pr(Winning next election) t-1")

# Vote share (t-1)
rdplot(data_candidateB$VPt_1[abs(data_candidateB$margin) <= bandwidthB], data_candidateB$margin[abs(data_candidateB$margin) <= bandwidthB],
       p = 1, kernel = "triangular",  
       x.label= "Margin of victory (t)",
       y.label = "Pr(Winning next election)")


# ALP incumbent running
rdplot(data_candidateB$inc[abs(data_candidateB$margin) <= bandwidthB], 
       data_candidateB$margin[abs(data_candidateB$margin) <= bandwidthB],
       p = 1, kernel = "triangular",  
       x.label= "Margin of victory (t)",
       y.label = "ALP incumbent")


# LIB/NAT incumbent running
rdplot(data_candidateB$incLIB[abs(data_candidateB$margin) <= bandwidthB], 
       data_candidateB$margin[abs(data_candidateB$margin) <= bandwidthB],
       p = 1, kernel = "triangular",  
       x.label= "Margin of victory (t)",
       y.label = "LIB/NAT incumbent")
```

Balance Tests on other electorate covariates ######################################################################

```{r}
library(eechidna)
data("abs2001")


abs2016$DivisionNm <- tools::toTitleCase(tolower(abs2016$DivisionNm))
abs2016$DivisionNm[abs2016$DivisionNm == "Mcewen"] <- "McEwen"
abs2016$DivisionNm[abs2016$DivisionNm == "Mcpherson"] <- "McPherson"
abs2016$DivisionNm[abs2016$DivisionNm == "Mcmillan"] <- "McMillan"
abs_2016 <- abs2016 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2016)


abs2013$DivisionNm <- tools::toTitleCase(tolower(abs2013$DivisionNm))
abs2013$DivisionNm[abs2013$DivisionNm == "Mcewen"] <- "McEwen"
abs2013$DivisionNm[abs2013$DivisionNm == "Mcpherson"] <- "McPherson"
abs2013$DivisionNm[abs2013$DivisionNm == "Mcmillan"] <- "McMillan"
abs_2013 <- abs2013 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2013)

abs2010$DivisionNm <- tools::toTitleCase(tolower(abs2010$DivisionNm))
abs2010$DivisionNm[abs2010$DivisionNm == "Mcewen"] <- "McEwen"
abs2010$DivisionNm[abs2010$DivisionNm == "Mcpherson"] <- "McPherson"
abs2010$DivisionNm[abs2010$DivisionNm == "Mcmillan"] <- "McMillan"
abs2010 <- abs2010 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2010)


abs2007$DivisionNm <- tools::toTitleCase(tolower(abs2007$DivisionNm))
abs2007$DivisionNm[abs2007$DivisionNm == "Mcewen"] <- "McEwen"
abs2007$DivisionNm[abs2007$DivisionNm == "Mcpherson"] <- "McPherson"
abs2007$DivisionNm[abs2007$DivisionNm == "Mcmillan"] <- "McMillan"
abs_2007 <- abs2007 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2007)


abs2004$DivisionNm <- tools::toTitleCase(tolower(abs2004$DivisionNm))
abs2004$DivisionNm[abs2004$DivisionNm == "Mcewen"] <- "McEwen"
abs2004$DivisionNm[abs2004$DivisionNm == "Mcpherson"] <- "McPherson"
abs2004$DivisionNm[abs2004$DivisionNm == "Mcmillan"] <- "McMillan"
abs_2004 <- abs2004 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2004)

abs2001$DivisionNm <- tools::toTitleCase(tolower(abs2001$DivisionNm))
abs2001$DivisionNm[abs2001$DivisionNm == "Mcewen"] <- "McEwen"
abs2001$DivisionNm[abs2001$DivisionNm == "Mcpherson"] <- "McPherson"
abs2001$DivisionNm[abs2001$DivisionNm == "Mcmillan"] <- "McMillan"
abs_2001 <- abs2001 %>% 
  select(DivisionNm, Indigenous, MedianHouseholdIncome, SocialServ, Unemployed, HighSchool, BornElsewhere) %>% 
  mutate(ElecYear = 2001)
```


SENSITIVITY TO BANDWIDTH CHOICE ##################################################################

```{r}
diff.bw <- c(0.01, 0.02, 0.03, 0.04, 0.05, 0.1, 0.15)

diff.bw.coef <- vector()
diff.bw.coef[1] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.01, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[2] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.02, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[3] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.03, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[4] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.04, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[5] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[6] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.1, cluster = data_candidateB$DivisionNm)$coef[2]
diff.bw.coef[7] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.15, cluster = data_candidateB$DivisionNm)$coef[2]

diff.bw.se.u <- vector()
diff.bw.se.u[1] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.01, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[2] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.02, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[3] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.03, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[4] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.04, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[5] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[6] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.1, cluster = data_candidateB$DivisionNm)$ci[3]
diff.bw.se.u[7] <- rdrobust(y=data_candidateB$Wint1, x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.15, cluster = data_candidateB$DivisionNm)$ci[3]


diff.bw.se.l <- vector()
diff.bw.se.l[1] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.01, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[2] <- rdrobust(y=data_candidateB$Wint1,
                            covs=data_candidateB$inc,
                            x=data_candidateB$margin,
                            kernel = "triangular",
           c=0, p = 1, h = 0.02, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[3] <- rdrobust(y=data_candidateB$Wint1,
                            covs=data_candidateB$inc,x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 1, h = 0.03, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[4] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.04, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[5] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.05, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[6] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.1, cluster = data_candidateB$DivisionNm)$ci[6]
diff.bw.se.l[7] <- rdrobust(y=data_candidateB$Wint1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.15, cluster = data_candidateB$DivisionNm)$ci[6]

diff.bw.data <- data.frame(Bandwidth = diff.bw, 
                           Coefficient = diff.bw.coef, 
                           CIU = diff.bw.se.u, 
                           CIL = diff.bw.se.l)
```

plot it
```{r}

ggplot(data= diff.bw.data, aes(x = Bandwidth, y= Coefficient)) +
  geom_point() +
  geom_errorbar(ymin=diff.bw.data$CIL, ymax=diff.bw.data$CIU, width = 0.001) +
  scale_y_continuous(limits = c(-2, 2)) +
  geom_hline(yintercept = 0, lty = 2, col = "red") +
  labs(x = "Bandwidth", y = "RD Estimate (Pr(Winning))", title = "Party-level: RD Estimates with Different Bandwidths") +
  theme_bw()
```



```{r}

summary(rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 5, cluster = data_candidateB$DivisionNm))
```




SENSITIVITY TO POLYNOMIAL CHOICE ##################################################################
```{r}
diff.ply <- c(1, 2, 3, 4, 5, 6)

diff.ply.coef <- vector()
diff.ply.coef[1] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, cluster = data_candidateB$DivisionNm)$coef[2]
diff.ply.coef[2] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 2, cluster = data_candidateB$DivisionNm)$coef[2]
diff.ply.coef[3] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 2, cluster = data_candidateB$DivisionNm)$coef[2]
diff.ply.coef[4] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 4, cluster = data_candidateB$DivisionNm)$coef[2]
diff.ply.coef[5] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 5, cluster = data_candidateB$DivisionNm)$coef[2]
diff.ply.coef[6] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 6, cluster = data_candidateB$DivisionNm)$coef[2]


diff.ply.se.u <- vector()
diff.ply.se.u[1] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1,  cluster = data_candidateB$DivisionNm)$ci[3]
diff.ply.se.u[2] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 2,  cluster = data_candidateB$DivisionNm)$ci[3]
diff.ply.se.u[3] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 3,cluster = data_candidateB$DivisionNm)$ci[3]
diff.ply.se.u[4] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 4, cluster = data_candidateB$DivisionNm)$ci[3]
diff.ply.se.u[5] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 5, cluster = data_candidateB$DivisionNm)$ci[3]
diff.ply.se.u[6] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 6,cluster = data_candidateB$DivisionNm)$ci[3]


diff.ply.se.l <- vector()
diff.ply.se.l[1] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1,  cluster = data_candidateB$DivisionNm)$ci[6]
diff.ply.se.l[2] <- rdrobust(y=data_candidateB$VPt1,
                            covs=data_candidateB$inc,
                            x=data_candidateB$margin,
                            kernel = "triangular",
           c=0, p = 2, cluster = data_candidateB$DivisionNm)$ci[6]
diff.ply.se.l[3] <- rdrobust(y=data_candidateB$VPt1,
                            covs=data_candidateB$inc,x=data_candidateB$margin,kernel = "triangular",
           c=0, p = 3, cluster = data_candidateB$DivisionNm)$ci[6]
diff.ply.se.l[4] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 4,  cluster = data_candidateB$DivisionNm)$ci[6]
diff.ply.se.l[5] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = ,  cluster = data_candidateB$DivisionNm)$ci[6]
diff.ply.se.l[6] <- rdrobust(y=data_candidateB$VPt1,
                            x=data_candidateB$margin,
                            covs=data_candidateB$inc,
                            kernel = "triangular",
           c=0, p = 1, h = 0.1, cluster = data_candidateB$DivisionNm)$ci[6]

diff.ply.data <- data.frame(Bandwidth = diff.ply, 
                           Coefficient = diff.ply.coef, 
                           CIU = diff.ply.se.u, 
                           CIL = diff.ply.se.l)
```


plot it
```{r}
ggplot(data= diff.ply.data, aes(x = Bandwidth, y= Coefficient)) +
  geom_point() +
  geom_errorbar(ymin=diff.ply.data$CIL, ymax=diff.ply.data$CIU, width = 0.1) +
  scale_y_continuous(limits = c(-0.15, .15)) +
  geom_hline(yintercept = 0, lty = 2, col = "red") +
  labs(x = "Polynomial Order", y = "RD Estimate, Vote Share (t+1)", title = "Party-level: RD Estimates Varying Order of Polynomial") +
  theme_bw()
```

DESCRIPTIVES ##################################################################

Correlation
```{r}
library(corrplot)

# reduced df
red <- data_candidateB %>% dplyr::select(margin, Wint1, VPt1, inc, incLIB, openseat, 
         Prev_TermsALP, Prev_TermsLIB, ALPsupport,
         spending, donations) %>% 
  data.frame() %>% 
  na.omit() 
red <- red[,-1]

cordata <- cor(red)

# change column and row names
rownames(cordata) <- c("Margin", "Win", "Vote Share", 
                       "Incumbent ALP", "Incumbent LIB/NAT", "Open Seat", 
                       "# Prev Terms", "# Prev Terms Opp", "Partisan Support",
                       "Spending", "Donations")
colnames(cordata) <- c("Margin", "Win", "Vote Share", 
                       "Incumbent ALP", "Incumbent LIB/NAT", "Open Seat", 
                       "# Prev Terms", "# Prev Terms Opp", "Partisan Support",
                       "Spending", "Donations")

# significance test with 95% confidence intervals
res <- cor.mtest(red, conf.level = .95)

corrplot(cordata, #p.mat = res$p,
#          insig = "label_sig",
#          pch.cex = .9, pch.col = "white",
         
         addCoef.col = "black",
         sig.level = c(.001, .01, .05),
         type = "lower",
         tl.col = "black",
         tl.srt = 45,
         method = "square",
         title = "",
         number.cex = .6)

```



Decline in party attachment over time
```{r}

```



```{r}
# government change in power over time?

# reelection - What's the re-election rate of elected representatives in Australia?

# length of service 


# total nubmer of candidates?
```












