---
title: "Bayesian Incumbency Advantage"
author: "Annie Chen"
date: "4/24/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# packages
pacman::p_load(brms, broom, tidyverse, modelr, tidybayes, bayesplot)

# ggplot theme
theme_set(theme_minimal())
```

<style type="text/css">
<!-- some custom styling -->
body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 10px;
}
h1.title {
  font-size: 42px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 32px;
  color: DarkBlue;
}
h2 { /* Header 2 */
  font-size: 26px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 22px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

# Data

```{r}
tpp_data <- read_csv("~/Dropbox/Thesis/inc_adv/clean_data/tpp_data.csv")

tpp_data <- tpp_data %>% 
  group_by(DivisionNm) %>% 
  mutate(# number of "trials" per DivisionNm
         total_years = n(), 
         # rescale incumbent predictor
         alp_incumbent = if_else(alp_incumbent == 1, 1, -1))
```


```{r}
get_prior(alp_win_t1 ~ 1 + alp_incumbent + (1 + alp_incumbent||DivisionNm),  
          data = tpp_data, 
          # this is the response distribution and link function
          family = binomial())
```


# Theoretical Model (DGP)

The outcome is a binary variable for whether an electorate votes for the ALP.

$$y_i \sim Binomial(n_i, p_i)$$
The probability of voting for ALP ($p$) varies by electorate $i$, varying intercept ($\alpha$) and varying slope ($\beta$), where the slope is the effect of incumbent status. The intercept is just the mean value of $p$ in each electorate:

$$logit(p_i) = \alpha_{electorate_{[i]}} + \beta_{electorate_{[i]}} Incumbent$$

Each parameter varies by researcher with a joint distribution of outcome from a Multivariate Normal, allowing to estimate the correlation between intercept and slope:
$$\begin{bmatrix}
\alpha_{researcher}\\ 
\beta_{researcher}\\ 
\end{bmatrix}
\sim 
MultvariateNormal\Big( 
\begin{bmatrix}
\alpha\\ 
\beta\\ 
\end{bmatrix}, \mathbf{S} 
\Big)$$

The prior means for the intercept and slope are weak (?), Normal centered at 0 and 10 variance. Better do prior predictive checks to make sure they are sensible:

```{r}
y <- tpp_data$alp_win_t1
yrep <- replicate(500, sample(x = y, size = length(y)))
brms::pp_check(y, yrep[1:50,], fun = ppc_dens_overlay)

x <- list(y = rnorm(50, 0, 10), yrep = matrix(rnorm(5000, 0, 10), nrow = 100, ncol = 50))
class(x) <- "foo"
pp_check.foo <- function(object, ..., type = c("multiple", "overlaid")) {
  y <- object[["y"]]
  yrep <- object[["yrep"]]
  switch(match.arg(type),
         multiple = ppc_hist(y, yrep[1:min(8, nrow(yrep)),, drop = FALSE]),
         overlaid = ppc_dens_overlay(y, yrep))
}
pp_check(x)
pp_check(x, type = "overlaid")
```



$$\alpha \sim Normal(0, 10)\\
\beta \sim Normal(0, 10)$$

Then, specify covariance structure of the joint distribution:
$$\mathbf{S} = 
\begin{pmatrix}
\sigma_{\alpha} & 0\\ 
0 & \sigma_{\beta}\\ 
\end{pmatrix} 
\mathbf{R}
\begin{pmatrix}
\sigma_{\alpha} & 0\\ 
0 & \sigma_{\beta}\\ 
\end{pmatrix}$$

In the covariance matrices, need specify the variances $\sigma$ as well.

$$(\sigma_{\alpha}, \sigma_{\beta}) \sim HalfCauchy(0, 10)\\
\mathbf{R} \sim LKJcorr(2)$$

# Estimation

### priors
```{r}
my_priors <- c(
    prior(normal(0, 10), class = Intercept, coef = ""),
    prior(cauchy(0, 10), class = sd),
    # prior for incumbency is 0.5 = no effect?
    prior(normal(0, 10), class = b),
    prior(lkj(2), class = cor)
    )
```


### model
```{r}
model2 <- brm(
  # double pipe if don't want to model correlation between intercept and slope
  # alp_win_t1 is if win in next year (number of successes)
  # total_years is number of years in each DivisionNm (total number of trials)
    alp_win_t1 | trials(total_years) ~ 1 + incumbent + (1 + incumbent|DivisionNm), 
    family = binomial(link = "logit"),
    # prior from previous fxn
    prior = my_priors,
    data = tpp_data,
    sample_prior = TRUE,
    # only 2 chains for speed, add more later
    chains = 2,
    # toss first 2000 in chain
    warmup = 2000, 
    # 10,000 iterations per chain
    iter = 1e4,
    # use all cores
    cores = parallel::detectCores(),
    # adjusting the delta step size (0.8 by default)
    control = list(adapt_delta = 0.95)
    )
```

# Analysis

`broom` output gives: `estimate` is the mean of the posterior distribution, `std.error`, and credible intervals (`upper`, `lower`) -- same with `brms::posterior_summary()`. Because this is a logistic model, the coefficients are in log-odds. If we exponentiate the slope (`b_incumbent`), you get the odds ratio for incumbency -- this can't be right...`exp(11.47)` times more likely to vote for party if it is incumbent!? That is with 95% HDI [`exp(6.24)`, `exp(21.14)`].

Interesting...reran model with two chains and got estimate of 7.18, this is probably not as robust as the one with 4 chains.

```{r}
# use broom for tidy output
#broom::tidy(model1, parameters = c("^b_", "cor", "^sd_"), prob = 0.95)

# or brms
posterior_summary(model2, 
                  # parameters: starts with b, sd, sigma
                  pars = c("^b_", "^sd_", "cor"), 
                  probs = c(0.025, 0.975) )

# average probability of winning...is close to 0? 
# retrieving the intercept
a <- fixef(model2)[1]
# transforming it back to the probability scale (equivalent to plogis(a))
exp(a) / (1 + exp(a) )

# effect of incumbency...is massive? 
# OR = exp(11.47)
fixef(model2)[2, c(1, 3, 4)] %>% exp
```


### plot diagnoses

#### Spaghetti plot
```{r eval = FALSE}
tpp_data %>%
    group_by(DivisionNm, total_years) %>%
  # generate an evenly spaced grid of points from the data
    modelr::data_grid(incumbent = seq_range(incumbent, n = 1e2) ) %>%
  # sample 100 fit lines from the posterior and overplot them
    tidybayes::add_fitted_samples(model2, newdata = ., n = 100, scale = "linear") %>%
    mutate(estimate = plogis(estimate) ) %>%
    ggplot(aes(x = incumbent, y = estimate, group = .iteration) ) +
    #geom_hline(yintercept = 0.5, lty = 2) +
    geom_line(aes(y = estimate, group = .iteration), size = 0.5, alpha = 0.1) +
    facet_wrap(~DivisionNm, nrow = 75) + # there are 150 DivisionNms...way too many to plot...
    theme_bw(base_size = 10) + labs(x = "Incumbent", y = "Estimate")
```


#### Histograms and Traceplots

Use traceplot to access the mixing of a chain

```{r}
#histogram and traceplots
model2 %>%
    plot(
        combo = c("hist", "trace"), widths = c(1, 1.5),
        theme = theme_bw(base_size = 12) )
```


## Hypothesis testing

The `brms::hypothesis()` function computes an evidence ratio (equivalent to a Bayes factor for point hypotheses, such as θ=0) -- nono-linear hypothesis testing of a `brmsfit` object. When testing point hypotheses, this evidence ratio is computed using the Savage-Dickey method.
 
```{r}
(hyp1 <- hypothesis(model2, 
                   class = "b",
                   hypothesis = "incumbent = 0"))
1 / hyp1$hypothesis$Evid.Ratio
```

### Compare the posterior to the prior

Interesting...the posterior is non-normal, a bit of a right tail.

```{r}
plot(hyp1, theme = theme_bw(base_size = 20) )

data.frame(prior = hyp1$prior_samples$H1, posterior = hyp1$samples$H1) %>%
    gather(type, value) %>%
    ggplot(aes(x = value) ) +
    geom_histogram(bins = 50, alpha = 0.8) +
    geom_vline(xintercept = 0, lty = 2, size = 1) +
    facet_wrap(~type, scales = "free") +
    xlab(expression(beta[incumbent]) ) +
    theme_bw(base_size = 20)
```


# Model Comparison

```{r}
bayes_factor(model2, model3)
```


# Posterior Predictive Checking (PPC)

Compare the observed data to data generated from the posterior distribution. (a generalization of NHST logic?)

Okay, the shapes look roughly similar, but the density looks off? Probably just a axis scale thing.

```{r}
# posterior density from data
tpp_data %>%
    ggplot(aes(x = alp_win_t1 / total_years) ) +
    geom_density(fill = "grey20") +
    theme_bw(base_size = 20)

# posterior generated from model, n = 100
pp_check(model2, nsamples = 1e2) + 
  theme_bw(base_size = 20)

pp_check(model2, nsamples = 1e2, type = "stat_2d") +
  theme_bw(base_size = 20)
```







